### 2020-09-01 benchmarking/benchmarkingVM/ESS_round5.tex
complete draft

% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:27:26
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 48.00,173.19) --
	(474.88,173.19);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.10,170.57) --
	( 54.10,160.89);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] ( 54.10,165.73) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.20,193.03) --
	( 60.20,169.27);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] ( 60.20,181.15) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.29,191.40) --
	( 66.29,174.61);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] ( 66.29,183.01) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.39,196.48) --
	( 72.39,170.97);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] ( 72.39,183.73) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.49,141.00) --
	( 78.49, 76.27);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] ( 78.49,108.63) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.59,183.38) --
	( 84.59,168.50);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] ( 84.59,175.94) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.69,170.18) --
	( 90.69,143.82);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] ( 90.69,157.00) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.79,196.84) --
	( 96.79,181.84);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] ( 96.79,189.34) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 54.10,169.09) --
	(102.88,169.09);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.49,284.14) {-1.5\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (108.98,  0.00) --
	(108.98,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.08,194.11) --
	(115.08,179.13);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (115.08,186.62) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.18,185.55) --
	(121.18,175.29);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (121.18,180.42) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.28,214.73) --
	(127.28,201.99);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (127.28,208.36) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.38,249.42) --
	(133.38,231.42);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (133.38,240.42) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.47,159.92) --
	(139.47,140.75);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (139.47,150.33) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.57,214.01) --
	(145.57,205.08);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (145.57,209.54) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.67,200.10) --
	(151.67,107.60);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (151.67,153.85) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.77,178.44) --
	(157.77,154.84);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (157.77,166.64) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (115.08,188.55) --
	(163.87,188.55);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.47,284.14) {5.7\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (169.97,  0.00) --
	(169.97,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.06,172.66) --
	(176.06,170.84);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (176.06,171.75) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.16,169.79) --
	(182.16,167.75);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (182.16,168.77) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.26,189.75) --
	(188.26,187.44);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (188.26,188.59) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.36,203.19) --
	(194.36,199.69);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (194.36,201.44) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.46,171.28) --
	(200.46,169.79);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (200.46,170.53) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.56,184.57) --
	(206.56,182.27);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (206.56,183.42) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.65,163.32) --
	(212.65,160.43);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (212.65,161.87) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.75,155.78) --
	(218.75,154.17);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (218.75,154.97) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (176.06,175.53) --
	(224.85,175.53);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.46,284.14) {0.84\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (230.95,  0.00) --
	(230.95,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.05,218.83) --
	(237.05,206.46);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (237.05,212.65) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.15,242.97) --
	(243.15,220.02);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (243.15,231.49) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.24,208.35) --
	(249.24,192.32);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (249.24,200.33) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.34,176.56) --
	(255.34,142.47);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (255.34,159.52) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,187.62) --
	(261.44,174.61);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (261.44,181.12) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.54,206.77) --
	(267.54,181.77);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (267.54,194.27) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.64,229.57) --
	(273.64,209.79);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (273.64,219.68) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.74,216.31) --
	(279.74,206.19);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (279.74,211.25) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.05,202.10) --
	(285.83,202.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (261.44,284.14) {11\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (291.93,  0.00) --
	(291.93,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.03,209.96) --
	(298.03,198.22);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (298.03,204.09) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.13,238.47) --
	(304.13,217.31);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (304.13,227.89) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.23,204.06) --
	(310.23,189.08);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (310.23,196.57) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.33,171.91) --
	(316.33,144.86);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (316.33,158.38) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.42,183.17) --
	(322.42,172.59);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (322.42,177.88) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.52,206.07) --
	(328.52,181.21);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (328.52,193.64) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.62,210.76) --
	(334.62,182.47);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (334.62,196.61) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.72,208.61) --
	(340.72,197.60);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (340.72,203.11) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.03,195.41) --
	(346.82,195.41);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (322.42,284.14) {8.3\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (352.92,  0.00) --
	(352.92,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.01,174.36) --
	(359.01,162.95);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (359.01,168.66) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.11,189.08) --
	(365.11,165.88);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (365.11,177.48) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.21,190.22) --
	(371.21,174.54);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (371.21,182.38) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.31,180.24) --
	(377.31,143.99);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (377.31,162.11) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.41,146.90) --
	(383.41,126.33);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (383.41,136.61) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.51,194.96) --
	(389.51,169.70);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (389.51,182.33) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-09-01 15:30:48
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 48.00,173.19) --
	(476.29,173.19);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.56,197.87) --
	( 53.56,173.22);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] ( 53.56,185.54) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.12,170.57) --
	( 59.12,160.89);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] ( 59.12,165.73) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 64.69,193.03) --
	( 64.69,169.27);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] ( 64.69,181.15) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.25,191.40) --
	( 70.25,174.61);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] ( 70.25,183.01) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.81,194.06) --
	( 75.81,177.12);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] ( 75.81,185.59) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.37,141.00) --
	( 81.37, 76.27);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] ( 81.37,108.63) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.94,183.38) --
	( 86.94,168.50);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] ( 86.94,175.94) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.50,170.18) --
	( 92.50,143.82);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] ( 92.50,157.00) circle (  2.25);
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.06,196.84) --
	( 98.06,181.84);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] ( 98.06,189.34) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 53.56,171.19) --
	(103.62,171.19);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.59,284.14) {0.72\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (109.18,  0.00) --
	(109.18,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.75,229.74) --
	(114.75,203.57);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (114.75,216.66) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.31,194.11) --
	(120.31,179.13);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (120.31,186.62) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.87,185.55) --
	(125.87,175.29);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (125.87,180.42) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.43,214.73) --
	(131.43,201.99);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (131.43,208.36) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.00,239.63) --
	(137.00,227.48);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (137.00,233.56) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.56,159.92) --
	(142.56,140.75);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (142.56,150.33) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.12,214.01) --
	(148.12,205.08);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (148.12,209.54) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.68,200.10) --
	(153.68,107.60);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (153.68,153.85) circle (  2.25);
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.24,178.44) --
	(159.24,154.84);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (159.24,166.64) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (114.75,190.92) --
	(164.81,190.92);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.78,284.14) {6.6\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (170.37,  0.00) --
	(170.37,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.93,168.43) --
	(175.93,160.62);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (175.93,164.53) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.49,172.66) --
	(181.49,170.84);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (181.49,171.75) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.05,169.79) --
	(187.05,167.75);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (187.05,168.77) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.62,189.75) --
	(192.62,187.44);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (192.62,188.59) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.18,201.95) --
	(198.18,198.81);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (198.18,200.38) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.74,171.28) --
	(203.74,169.79);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (203.74,170.53) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.30,184.57) --
	(209.30,182.27);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (209.30,183.42) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.87,163.32) --
	(214.87,160.43);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (214.87,161.87) circle (  2.25);
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.43,155.78) --
	(220.43,154.17);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (220.43,154.97) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (175.93,174.20) --
	(225.99,174.20);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.96,284.14) {0.36\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (231.55,  0.00) --
	(231.55,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.11,171.43) --
	(237.11,152.78);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (237.11,162.10) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.68,218.83) --
	(242.68,206.46);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (242.68,212.65) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.24,242.97) --
	(248.24,220.02);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (248.24,231.49) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.80,208.35) --
	(253.80,192.32);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (253.80,200.33) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.36,179.26) --
	(259.36,152.83);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (259.36,166.04) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.93,187.62) --
	(264.93,174.61);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (264.93,181.12) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (270.49,206.77) --
	(270.49,181.77);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (270.49,194.27) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.05,229.57) --
	(276.05,209.79);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (276.05,219.68) circle (  2.25);
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (281.61,216.31) --
	(281.61,206.19);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (281.61,211.25) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.11,198.57) --
	(287.17,198.57);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (262.14,284.14) {9.5\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (292.74,  0.00) --
	(292.74,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.30,166.69) --
	(298.30,150.30);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (298.30,158.50) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (303.86,209.96) --
	(303.86,198.22);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (303.86,204.09) circle (  2.25);
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (309.42,238.47) --
	(309.42,217.31);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (309.42,227.89) circle (  2.25);
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (314.99,204.06) --
	(314.99,189.08);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (314.99,196.57) circle (  2.25);
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (320.55,183.38) --
	(320.55,154.32);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (320.55,168.85) circle (  2.25);
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (326.11,183.17) --
	(326.11,172.59);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (326.11,177.88) circle (  2.25);
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.67,206.07) --
	(331.67,181.21);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (331.67,193.64) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (337.23,210.76) --
	(337.23,182.47);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (337.23,196.61) circle (  2.25);
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.80,208.61) --
	(342.80,197.60);
\definecolor{fillColor}{RGB}{68,68,68}

\path[fill=fillColor] (342.80,203.11) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.30,192.59) --
	(348.36,192.59);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (323.33,284.14) {7.2\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (353.92,  0.00) --
	(353.92,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.48,175.89) --
	(359.48,161.24);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (359.48,168.57) circle (  2.25);
\definecolor{drawColor}{RGB}{253,104,0}
